Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
conclusion

>>>>

\section{Conclusion}

The \naive Bayes and decision tree classifiers are not smart enough to sort out
a large number of features when the data sets are of small or moderate size,
which requires judicious choosing of features.  Co-occurrence, base word and
collocation with part of speech collocation seem to be more powerful features
than dependency parsing, and bootstrapping on the data in an attempt to get a
larger training base was ineffective because precision was too low.
